An open library of human kinase domain constructs for automated bacterial expression

### 2017-10-04 manuscript/manuscript_old/ms.tex
adding in an excel spreadsheet summarizing the data

Human protein kinases were selected by querying the UniProt API for any human protein with a domain containing the string "protein kinase", and which was manually annotated and reviewed (i.e. a Swiss-Prot entry).
The query string used was:\\
{\tt taxonomy:"Homo sapiens (Human) [9606]" AND domain:"protein kinase" AND reviewed:yes}\\
Data was returned by the UniProt API in XML format and contained protein sequences and relevant PDB structures, along with many other types of genomic and functional information.
To select active protein kinase domains, the UniProt domain annotations were searched using the regular expression {\tt \^{}Protein kinase(?!; truncated)(?!; inactive)}, which excludes certain domains annotated "Protein kinase; truncated" and "Protein kinase; inactive".
Sequences for the selected domains were then stored.
The sequences were derived from the canonical isoform as determined by UniProt.

>>>>

Human protein kinases were selected by querying the UniProt API (query date 30 May 2014) for any human protein with a domain containing the string "protein kinase", and which was manually annotated and reviewed (i.e. a Swiss-Prot entry).
The query string used was:\\
{\tt taxonomy:"Homo sapiens (Human) [9606]" AND domain:"protein kinase" AND reviewed:yes}\\
Data was returned by the UniProt API in XML format and contained protein sequences and relevant PDB structures, along with many other types of genomic and functional information.
To select active protein kinase domains, the UniProt domain annotations were searched using the regular expression {\tt \^{}Protein kinase(?!; truncated)(?!; inactive)}, which excludes certain domains annotated "Protein kinase; truncated" and "Protein kinase; inactive".
Sequences for the selected domains were then stored.
The sequences were derived from the canonical isoform as determined by UniProt.
